---
title: "MUSA 508 Predicting Risk HW"
author: "Liz Williams"
date: "October 23rd, 2020"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

library(tidyverse)
library(sf)
library(RSocrata)
library(viridis)
library(spatstat)
library(raster)
library(spdep)
library(FNN)
library(grid)
library(gridExtra)
library(knitr)
library(kableExtra)
library(tidycensus)
# functions
root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

qBr <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(quantile(round(df[[variable]],0),
                          c(.01,.2,.4,.6,.8), na.rm=T))
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]]), digits = 3),
                 c(.01,.2,.4,.6,.8), na.rm=T)
  }
}
q5 <- function(variable) {as.factor(ntile(variable, 5))}

palette5 <- c("#f0f9e8","#bae4bc","#7bccc4","#43a2ca","#0868ac")

nn_function <- function(measureFrom,measureTo,k) {
  measureFrom_Matrix <-
    as.matrix(measureFrom)
  measureTo_Matrix <-
    as.matrix(measureTo)
  nn <-   
    get.knnx(measureTo, measureFrom, k)$nn.dist
    output <-
      as.data.frame(nn) %>%
      rownames_to_column(var = "thisPoint") %>%
      gather(points, point_distance, V1:ncol(.)) %>%
      arrange(as.numeric(thisPoint)) %>%
      group_by(thisPoint) %>%
      summarize(pointDistance = mean(point_distance)) %>%
      arrange(as.numeric(thisPoint)) %>% 
      dplyr::select(-thisPoint) %>%
      pull()
  
  return(output)  
}

## Load API Key - Liz
census_api_key("d8b938a81d19a2811d021f339295fbf6135f7d36", overwrite = TRUE)

## Load API Key - Sabrina 
census_api_key("30bae866445f7bea5ea57b8f5fba60b11b8b145e", overwrite = TRUE)
```

# Setup 
## Read in the data from DC

```{r}

robberies <- st_read("https://opendata.arcgis.com/datasets/6af5cb8dc38e4bcbac8168b27ee104aa_38.geojson") %>%
  filter(OFFENSE == "ROBBERY") %>%
  mutate(LATITUDE = as.numeric(LATITUDE),LONGITUDE = as.numeric(LONGITUDE)) %>% 
  dplyr::select(LATITUDE, LONGITUDE) %>%
  na.omit() %>%
  st_as_sf(coords = c("LATITUDE", "LONGITUDE"), crs = 4326, agr = "constant")%>%
  st_transform('ESRI:102685') %>%
  distinct()

DCboundary <- st_read("https://opendata.arcgis.com/datasets/7241f6d500b44288ad983f0942b39663_10.geojson") %>%
    st_transform('ESRI:102685')
  
PoliceServiceAreas <- st_read("https://opendata.arcgis.com/datasets/db24f3b7de994501aea97ce05a50547e_10.geojson") %>%
    st_transform('ESRI:102685')

tracts17 <- 
  get_acs(geography = "tract", variables = c("B01001_001E","B01001A_001E","B06011_001"), 
          year = 2017, state=11, geometry=T, output = "wide") %>%
  st_transform(st_crs(DCboundary))  %>%
  rename(TotalPop = B01001_001E,
         NumberWhites = B01001A_001E,
         Median_Income = B06011_001E) %>%
  mutate(percentWhite = ((NumberWhites / TotalPop)*100),
         raceContext = ifelse(percentWhite > .5, "Majority White", "Majority Non-White"),
         incomeContext = ifelse(Median_Income > 32322, "High Income", "Low Income"))

tracts18 <- 
  get_acs(geography = "tract", variables = c("B01001_001E","B01001A_001E","B06011_001"), 
          year = 2018, state=11, geometry=T, output = "wide") %>%
  st_transform(st_crs(DCboundary))  %>%
  rename(TotalPop = B01001_001E,
         NumberWhites = B01001A_001E,
         Median_Income = B06011_001E) %>%
  mutate(percentWhite = ((NumberWhites / TotalPop)*100),
         raceContext = ifelse(percentWhite > .5, "Majority White", "Majority Non-White"),
         incomeContext = ifelse(Median_Income > 32322, "High Income", "Low Income"))

requests311 <- st_read("https://opendata.arcgis.com/datasets/19905e2b0e1140ec9ce8437776feb595_8.geojson") %>%
    st_transform('ESRI:102685')

graffiti <- requests311 %>%
  filter(SERVICECODEDESCRIPTION == "Graffiti Removal") %>%
  dplyr::select(geometry) %>%
  mutate(Legend = "Graffiti_Removal")

streetlights <- requests311 %>%
  filter(SERVICECODEDESCRIPTION == "Streetlight Repair Investigation") %>%
  dplyr::select(geometry) %>%
  mutate(Legend = "Streelight_Out")

abandonedCar <- requests311 %>%
  filter(SERVICECODEDESCRIPTION %in% c("Abandoned Vehicle - On Public Property", "	
Abandoned Vehicle - On Private Property")) %>%
  dplyr::select(geometry) %>%
  mutate(Legend = "Abandoned_Car")

sanitation <- requests311 %>%
  filter(SERVICECODEDESCRIPTION == "Sanitation Enforcement") %>%
  dplyr::select(geometry) %>%
  mutate(Legend = "Sanitation")

illegalDumping <- requests311 %>%
  filter(SERVICECODEDESCRIPTION == "Illegal Dumping") %>%
  dplyr::select(geometry) %>%
  mutate(Legend = "Illegal_Dumping")

homelessServices <- requests311 %>%
  filter(SERVICECODEDESCRIPTION == "Homeless Services - Winter/Hypothermia Season") %>%
  dplyr::select(geometry) %>%
  mutate(Legend = "Homeless_Services")

gunshots <- st_read("https://opendata.arcgis.com/datasets/89bfd2aed9a142249225a638448a5276_29.geojson") %>%
    st_transform('ESRI:102685') %>%
    dplyr::select(geometry) %>%
    mutate(Legend = "Gun_Shots")

green_spaces <- st_read("https://opendata.arcgis.com/datasets/9927e456ac024b11811323812934edbb_12.geojson") %>%
    st_transform('ESRI:102685') %>%
    dplyr::select(geometry) %>%
    mutate(Legend = "Green_Space")

police_stations <- st_read("https://opendata.arcgis.com/datasets/9e465c1e6dfd4605a7632ed5737644f3_11.geojson")%>%
    st_transform('ESRI:102685')

neighborhoods <- st_read("https://opendata.arcgis.com/datasets/f6c703ebe2534fc3800609a07bad8f5b_17.geojson") %>%
    st_transform('ESRI:102685')

public_housing_areas <- st_read("https://opendata.arcgis.com/datasets/7f40eee5afaa4210959c2a55328a0cab_15.geojson") %>%
    st_transform('ESRI:102685') %>%
    dplyr::select(geometry) %>%
    mutate(Legend = "public_housing_areas")

```

## Make the fishnet
```{r}
## using {sf} to create the grid
## Note the `.[DCBoundary] %>% ` line. This is needed to clip the grid to our data
fishnet <- 
  st_make_grid(DCboundary,
               cellsize = 500, 
               square = TRUE) %>%
  #.[DCboundary] %>% ## had to add (not in book?) - gets rid of those things in box                           not intersecting boundary
  st_sf() %>%
  mutate(uniqueID = rownames(.))
```

# A map of your outcome of interest in point form, with some description of what, when, and why you think selection bias may be an issue.

```{r}
ggplot() + 
  geom_sf(data=DCboundary) +
  geom_sf(data=robberies, size=.7) +
  labs(title = "DC Robberies in 2017") +
  mapTheme()

ggplot(tracts17) + 
  geom_sf(aes(fill = q5(percentWhite))) +
  geom_sf(data=robberies, size=.4) +
  scale_fill_manual(values = palette5,labels = qBr(tracts17, "percentWhite"),name = "Percent White\n(Quintile Breaks)") +
  labs(title = "DC Robberies in 2017") +
  mapTheme()

```

# A map of your outcome joined to the fishnet.

```{r}
## add a value of 1 to each crime, sum them with aggregate
crime_net <- 
  dplyr::select(robberies) %>% 
  mutate(countRobberies = 1) %>% 
  aggregate(., fishnet, sum) %>%
  mutate(countRobberies = replace_na(countRobberies, 0),
         uniqueID = rownames(.),
         cvID = sample(round(nrow(fishnet) / 24), 
                       size=nrow(fishnet), replace = TRUE))

ggplot() +
  geom_sf(data = crime_net, aes(fill = countRobberies), color = NA) +
  scale_fill_viridis() +
  labs(title = "Count of Vandalism Incidents for the fishnet") +
  mapTheme()
```

# A small multiple map of your risk factors in the fishnet (counts, distance and/or other feature engineering approaches).

```{r}

vars_net <- 
  rbind(abandonedCar, gunshots, sanitation, 
        streetlights, graffiti, green_spaces) %>%
  st_join(., fishnet, join=st_within) %>%
  st_drop_geometry() %>%
  group_by(uniqueID, Legend) %>%
  summarize(count = n()) %>%
    full_join(fishnet) %>%
    spread(Legend, count, fill=0) %>%
    st_sf() %>%
    dplyr::select(-`<NA>`) %>%
    na.omit() %>%
    ungroup()

vars_net.long <- 
  gather(vars_net, Variable, value, -geometry, -uniqueID)

vars <- unique(vars_net.long$Variable)
mapList <- list()

for(i in vars){
  mapList[[i]] <- 
    ggplot() +
      geom_sf(data = filter(vars_net.long, Variable == i), aes(fill=value), colour=NA) +
      scale_fill_viridis(name="") +
      labs(title=i) +
      mapTheme()}

do.call(grid.arrange,c(mapList, ncol =3, top = "Risk Factors by Fishnet"))

```

## nn distance 

```{r}
st_c <- st_coordinates
st_coid <- st_centroid

vars_net <-
  vars_net %>%
    mutate(
      abandonedCar.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(abandonedCar),3),
      gunshots.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(gunshots),3),
      graffiti.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(graffiti),3),
      green_spaces.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(green_spaces),3),
      streetlights.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(streetlights),3),
      sanitation.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(sanitation),3))

vars_net.long.nn <- 
  dplyr::select(vars_net, ends_with(".nn")) %>%
    gather(Variable, value, -geometry)

vars <- unique(vars_net.long.nn$Variable)
mapList <- list()

for(i in vars){
  mapList[[i]] <- 
    ggplot() +
      geom_sf(data = filter(vars_net.long.nn, Variable == i), aes(fill=value), colour=NA) +
      scale_fill_viridis(name="") +
      labs(title=i) +
      mapTheme()}

do.call(grid.arrange,c(mapList, ncol = 3, top = "Nearest Neighbor risk Factors by Fishnet"))

```

## Add distance to downtown as a feature

```{r}
downtownPoint <-
  filter(neighborhoods, NAME == "Cluster 8") %>%
  st_centroid()

vars_net$downtownDistance =
  st_distance(st_centroid(vars_net),downtownPoint) %>%
  as.numeric() 

vars_net.long <- 
  gather(vars_net, Variable, value, -geometry, -uniqueID)

ggplot() +
      geom_sf(data = filter(vars_net.long, Variable == "downtownDistance"), aes(fill=value), colour=NA) +
      scale_fill_viridis(name="") +
      labs(title="Distance to downtown") +
      mapTheme()

```

## Create the final net
```{r}
final_net <-
  left_join(crime_net, st_drop_geometry(vars_net), by="uniqueID") 

final_net <-
  st_centroid(final_net) %>%
    st_join(dplyr::select(neighborhoods, NBH_NAMES)) %>%
    st_join(dplyr::select(PoliceServiceAreas, PSA)) %>%
      st_drop_geometry() %>%
      left_join(dplyr::select(final_net, geometry, uniqueID)) %>%
      st_sf() %>%
  na.omit()
```

# Local Moran's I-related small multiple map of your outcome (see 4.1)

```{r}
final_net.nb <- poly2nb(as_Spatial(final_net), queen=TRUE)
final_net.weights <- nb2listw(final_net.nb, style="W", zero.policy=TRUE)

final_net.localMorans <- 
  cbind(
    as.data.frame(localmoran(final_net$countRobberies, final_net.weights)),
    as.data.frame(final_net)) %>% 
    st_sf() %>%
      dplyr::select(Robbery_Count = countRobberies, 
                    Local_Morans_I = Ii, 
                    P_Value = `Pr(z > 0)`) %>%
      mutate(Significant_Hotspots = ifelse(P_Value <= 0.01, 1, 0)) %>%
      gather(Variable, Value, -geometry)
  
vars <- unique(final_net.localMorans$Variable)
varList <- list()

for(i in vars){
  varList[[i]] <- 
    ggplot() +
      geom_sf(data = filter(final_net.localMorans, Variable == i), 
              aes(fill = Value), colour=NA) +
      scale_fill_viridis(name="") +
      labs(title=i) +
      mapTheme() + theme(legend.position="bottom")}

do.call(grid.arrange,c(varList, ncol = 4, top = "Local Morans I statistics, Burglary"))

```

Here, the null hypothesis is that the burglary count at a given location is randomly distributed relative to its immediate neighbors.

# A small multiple scatterplot with correlations.

```{r}
final_net <-
  final_net %>% 
  mutate(robbery.isSig = 
           ifelse(localmoran(final_net$countRobberies, 
                             final_net.weights)[,5] <= 0.0000001, 1, 0)) %>%
  mutate(robbery.isSig.dist = 
           nn_function(st_coordinates(st_centroid(final_net)),
                       st_coordinates(st_centroid(
                         filter(final_net, robbery.isSig == 1))), 1))
```


```{r, fig.width=5, fig.height=6}

correlation.long <-
  st_drop_geometry(final_net) %>%
    dplyr::select(-uniqueID, -cvID, -downtownDistance, -NBH_NAMES, -PSA) %>%
    gather(Variable, Value, -countRobberies)

correlation.cor <-
  correlation.long %>%
    group_by(Variable) %>%
    summarize(correlation = cor(Value, countRobberies, use = "complete.obs"))
    
ggplot(correlation.long, aes(Value, countRobberies)) +
  geom_point(size = 0.5) +
  facet_wrap(~Variable, ncol = 2, scales = "free") +
  geom_text(data = correlation.cor, aes(label = paste("r =", round(correlation, 2))),
            x=-Inf, y=Inf, vjust = 1.5, hjust = -.1) +
  geom_smooth(method = "lm", se = FALSE, colour = "orange") +
  facet_wrap(~Variable, ncol = 2, scales = "free") +
  labs(title = "Burglary count as a function of risk factors") +
  plotTheme()
```

# A histogram of your dependent variable.

```{r}

final_net %>%
  ggplot(aes(countRobberies)) + 
    geom_histogram(bins = 5, colour="black") +
  scale_x_continuous(breaks = seq(0, 5, by = 1)) + 
    labs(title="Distribution of Robbery Counts", 
         x="countRobberies", y="Count") 
```

# A small multiple map of model errors by random k-fold and spatial cross validation.

## Setup cross validation
```{r}

# Below, goodness of fit metrics are generated for four regressions - two including Just Risk Factors (reg.vars), and a second (reg.ss.vars) includes risk factors plus the Local Moran's I 

reg.vars <- c("abandonedCar.nn", "gunshots.nn", "graffiti.nn", 
              "green_spaces.nn", "streetlights.nn", "sanitation.nn", 
              "downtownDistance")

reg.ss.vars <- c("abandonedCar.nn", "gunshots.nn", "graffiti.nn", 
              "green_spaces.nn", "streetlights.nn", "sanitation.nn", 
              "downtownDistance", "robbery.isSig", "robbery.isSig.dist")
```


```{r}

# setup cross validate function
crossValidate <- function(dataset, id, dependentVariable, indVariables) {

allPredictions <- data.frame()
cvID_list <- unique(dataset[[id]])

for (i in cvID_list) {

  thisFold <- i
  cat("This hold out fold is", thisFold, "\n")

  fold.train <- filter(dataset, dataset[[id]] != thisFold) %>% as.data.frame() %>% 
                dplyr::select(id, geometry, indVariables, dependentVariable)
  fold.test  <- filter(dataset, dataset[[id]] == thisFold) %>% as.data.frame() %>% 
                dplyr::select(id, geometry, indVariables, dependentVariable)
  
  regression <-
    glm(countRobberies ~ ., family = "poisson", 
      data = fold.train %>% 
      dplyr::select(-geometry, -id))
  
  thisPrediction <- 
    mutate(fold.test, Prediction = predict(regression, fold.test, type = "response"))
    
  allPredictions <-
    rbind(allPredictions, thisPrediction)
    
  }
  return(st_sf(allPredictions))
}
```

## Cross validation

```{r}
reg.cv <- crossValidate(
  dataset = final_net,
  id = "cvID",
  dependentVariable = "countRobberies",
  indVariables = reg.vars) %>%
    dplyr::select(cvID = cvID, countRobberies, Prediction, geometry)

reg.ss.cv <- crossValidate(
  dataset = final_net,
  id = "cvID",
  dependentVariable = "countRobberies",
  indVariables = reg.ss.vars) %>%
    dplyr::select(cvID = cvID, countRobberies, Prediction, geometry)
  
reg.spatialCV <- crossValidate(
  dataset = final_net,
  id = "NBH_NAMES",
  dependentVariable = "countRobberies",
  indVariables = reg.vars) %>%
    dplyr::select(cvID = NBH_NAMES, countRobberies, Prediction, geometry)

reg.ss.spatialCV <- crossValidate(
  dataset = final_net,
  id = "NBH_NAMES",
  dependentVariable = "countRobberies",
  indVariables = reg.ss.vars) %>%
    dplyr::select(cvID = NBH_NAMES, countRobberies, Prediction, geometry)
```

## Cross validation metrics

```{r}
reg.summary <- 
  rbind(
    mutate(reg.cv,           Error = Prediction - countRobberies,
                             Regression = "Random k-fold CV: Just Risk Factors"),
                             
    mutate(reg.ss.cv,        Error = Prediction - countRobberies,
                             Regression = "Random k-fold CV: Spatial Process"),
    
    mutate(reg.spatialCV,    Error = Prediction - countRobberies,
                             Regression = "Spatial LOGO-CV: Just Risk Factors"),
                             
    mutate(reg.ss.spatialCV, Error = Prediction - countRobberies,
                             Regression = "Spatial LOGO-CV: Spatial Process")) %>%
    st_sf() 
```

```{r}
error_by_reg_and_fold <- 
  reg.summary %>%
    group_by(Regression, cvID) %>% 
    summarize(Mean_Error = mean(Prediction - countRobberies, na.rm = T),
              MAE = mean(abs(Mean_Error), na.rm = T),
              SD_MAE = mean(abs(Mean_Error), na.rm = T)) %>%
  ungroup()

error_by_reg_and_fold %>%
  ggplot(aes(MAE)) + 
    geom_histogram(bins = 30, colour="black", fill = "#FDE725FF") +
    facet_wrap(~Regression) +  
    geom_vline(xintercept = 0) + scale_x_continuous(breaks = seq(0, 8, by = 1)) + 
    labs(title="Distribution of MAE", subtitle = "k-fold cross validation vs. LOGO-CV",
         x="Mean Absolute Error", y="Count") 
```


# A table of MAE and standard deviation MAE by regression.

```{r}
st_drop_geometry(error_by_reg_and_fold) %>%
  group_by(Regression) %>% 
    summarize(Mean_MAE = round(mean(MAE), 2),
              SD_MAE = round(sd(MAE), 2)) %>%
  kable(caption = "MAE by regression") %>%
    kable_styling("striped", full_width = F) %>%
    row_spec(2, color = "black", background = "#FDE725FF") %>%
    row_spec(4, color = "black", background = "#FDE725FF") 
```

# A table of raw errors by race context for a random k-fold vs. spatial cross validation regression.

```{r}
reg.summary %>% 
  filter(str_detect(Regression, "LOGO")) %>%
    st_centroid() %>%
    st_join(tracts18) %>%
    na.omit() %>%
      st_drop_geometry() %>%
      group_by(Regression, raceContext) %>%
      summarize(mean.Error = mean(Error, na.rm = T)) %>%
      spread(raceContext, mean.Error) %>%
      kable(caption = "Mean Error by neighborhood racial context") %>%
        kable_styling("striped", full_width = F) 
```


# The map comparing kernel density to risk predictions for the next year's crime.
```{r}
# Download 2018 robberies
robberies18 <- st_read("https://opendata.arcgis.com/datasets/38ba41dd74354563bce28a359b59324e_0.geojson") %>%
  filter(OFFENSE == "ROBBERY") %>%
  mutate(LATITUDE = as.numeric(LATITUDE),LONGITUDE = as.numeric(LONGITUDE)) %>% 
  dplyr::select(LATITUDE, LONGITUDE) %>%
  na.omit() %>%
  st_as_sf(coords = c("LATITUDE", "LONGITUDE"), crs = 4326, agr = "constant")%>%
  st_transform('ESRI:102685') %>%
  distinct() %>%
   .[fishnet,] #idk what this line does??

```

# The bar plot making this comparison.

# Two paragraphs on why or why not you would recommend your algorithm be put into production.

